Corotating Dust Clumps Around Adolescent M-Dwarfs: Four Years of TESS

### 2023-06-26 paper/ms.tex
update ms

\begin{figure*}[!t]
	\begin{center}
		\subfloat{
			\includegraphics[width=0.8\textwidth]{lc_mosaic_fav3.pdf}
		}

		\vspace{-0.4cm}
		\subfloat{
			\includegraphics[width=0.8\textwidth]{models.pdf}
		}
	\end{center}
	\caption{
		{\bf Complex quasiperiodic variables (CQVs)}:
		{\it Top:} Phase-folded TESS light curves of three CQVs.  Each is
		stacked over one month.  Gray are raw 2-minute data; black bins to
		300 points per cycle.  Periods in hours are in the bottom right of
		each panel.  In order left-to-right, the objects are LP 12-502
		(TIC 402980664; Sector~19), TIC 94088626 (Sector 10), and TIC
		425933644 (Sector~28).
		{\it Bottom:} Plausible cartoon models for the phenomenon.  The
		dust clump scenario seems most plausible, given
		the stability of the phenomenon, the lack of observed infrared
		excesses, and the challenge of producing broadband opacity variations
		with only ionized hydrogen in the prominence scenario.
	}
	\label{fig:f1}
\end{figure*}

>>>>

\begin{figure*}[!t]
	\begin{center}
		\subfloat{
			\includegraphics[width=0.8\textwidth]{f1a.pdf}
		}

		\vspace{-0.45cm}
		\subfloat{
			\includegraphics[width=0.8\textwidth]{f1b.pdf}
		}
	\end{center}
		\vspace{-0.2cm}
	\caption{
		{\bf Complex quasiperiodic variables (CQVs)}:
		{\it Top:} Phase-folded TESS light curves of three CQVs.  Each is
		stacked over one month.  Gray are raw 2-minute data; black bins to
		300 points per cycle.  Periods in hours are in the bottom right of
		each panel.  In order left-to-right, the objects are LP 12-502
		(TIC 402980664; Sector~19), TIC 94088626 (Sector 10), and TIC
		425933644 (Sector~28).
		{\it Bottom:} Plausible cartoon models for the phenomenon.  The
		dust clump scenario seems most plausible, given
		the stability of the dips, the lack of observed infrared
		excesses, and the challenge of producing broadband opacity variations
		with only ionized hydrogen in the prominence scenario.
	}
	\label{fig:f1}
\end{figure*}
